Presentation Title

### 2017-08-07 thesis/chapters/ch6-conclusion.tex
Fixes

In this work we introduced an application neutral blockchain system which we call Checo.
We add checkpoint block to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
Nodes make transactions via the transaction protocol,
which is adapted from an existing work called True Halves.
We introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

@@

Our experiment is carried out in a somewhat idealised world (DAS-5).
To understand our system further, we hope to experiment with a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the TrustChain in Tribler stores the number of bytes uploaded and downloaded between users, but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly, it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

>>>>

In this work we introduced an application neutral blockchain system which we call Checo.
We add checkpoint block to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result, which is a set of checkpoint blocks, lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

@@

Our experiment is carried out in a somewhat idealised world (DAS-5).
We hope to experiment our prototype in a more realistic environment.
For example, DeterLab~\cite{mirkovic2012teaching} lets users simulate network delay,
which is important for discovering issue that may only occur in hostile environments.
To understand our system further, we hope to experiment with a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the TrustChain in Tribler stores the number of bytes uploaded and downloaded between users, but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly, it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

### 2017-08-07 thesis/formalities/preface.tex
Fixes

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
I mined my first Bitcoin in early 2013 with a GPU.
Since then, I have been interested in decentralising the traditionally centralised systems.
Following the Snowden revelations, the interest became a burning desire.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.

>>>>

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, when I mined my first Bitcoin, 
I have been interested in decentralising the traditionally centralised systems.
Following the Snowden revelations, the interest became a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.
